`SimSurvey`: an `R` package for comparing the design and analysis of surveys by simulating spatially-correlated populations

### 2020-04-15 analysis/paper/response_letter.Rmd

Reviewer #1: This is my second time reviewing this manuscript and the authors did a great job addressing people's comments. Great job for that. The manuscript is now much clearer and read well, I think.

*We thank the reviewer for the kind words.*

This time, I only have a few minor comments:  
L19 : «there is a limited number of»

*We have removed the 'the' that should not have been in that sentence.*

@@

L103: Maybe it would be a good idea to justify why you are converting to abundance at length.

*Agreed, we have started a new paragraph regarding abundance at length which begins: "In practice, abundance at age is often inferred from length data as it is easier to collect. Abundance at length is therefore simulated from abundance at age using the original von Bertalanffy growth curve"*

@@

L240-242: I think it could be a good idea to show how to exactly do this (maybe obvious to advanced people but not to the general audience). This could be a simple reference to an example on the github repo.

*Indeed, this is a helpful idea and we have now created a short vignette on creating closures and this can be accessed via the pkgdown site (https://paulregular.github.io/SimSurvey/articles/custom_closures.html). A link to this vignette has been added to the paper.*

@@

Table 2: If bias correction was not implemented, I would suggest to change the labeling in the table here and elsewhere (if needed) and replace the “mean” by “median” (if the variable is transformed back to the original scale). If not, I would make clear that you talk about mean in log scale.

*Good catch, we have added log after mean to ensure that readers know the functions are operating in log scale.*

@@

L326: I did not see how one can use INLA or RandomFields in Appendix S3. This is a similar comment as the one for line 240-242.

*We have added the following in parentheses: see the code behind `sim_ays_covar_sped` [https://github.com/PaulRegular/SimSurvey/blob/master/R/sim_dist_spde.R] for an example of how the `sim_ays_covar` closure was modified to apply a Stochastic Partial Differential Equation approach using the `INLA` package.*

@@

L481-490: the processing time is surprisingly long… it is not an issue in itself but this might refrain some people to using this package… I think some code optimization could help (e.g. vectorize, use matrix operation as much as possible, etc)

*We have stretched our programming skills to the limit to reduce the processing time as much as possible. Of course, said programming skills are largely self-taught, so there is surely room for improvement. While developing the package, we repeatedly profiled our code and vectorized as much as we could, leaning heavily on the `data.table` package. We have also applied parallel processing in places in an attempt to speed up the code. Another step to further optimize the code would be to translate many of the core functions to C++, however this is on the wish list and well outside the scope of the project at this point in time. We are hopeful that we have produced enough here to catalyze collaborations that help extend and optimize the package.*

### 2020-04-15 analysis/paper/sim_survey_paper.Rmd
Expand README and add some structure to pkgdown reference page
Complete draft of response letter and revised paper

library(SimSurvey)
library(plotly)
library(raster)
library(lattice)
library(viridis)
library(data.table)
library(magrittr)
Sys.setenv("MAPBOX_TOKEN" = "pk.eyJ1IjoicGF1bHJlZ3VsYXIiLCJhIjoiY2pueGIxejMxMGM0MjNqbjR1aXdwYm92bSJ9.R-t1SCa0VHKf4N-PQmYI5Q")
source("analysis/paper/helper_functions.R")

@@

Here, the `R_vec` object holds 100 years of simulated recruitment values and each run of the `R_fun` function will result in different simulated values using the internal formulation and the parameters supplied to `sim_R`. The other closures included in the package operate in a similar way in that parameter inputs are supplied to the closure and the functions returned by the closure requires inputs such as ages and/or years. This was done to avoid the repeated specifications of key arguments, such as ages and years. Moreover, this approach provides an option for advanced R users to inspect and modify the closures implemented in the package to supply custom closures with alternate equations. ... . Also note that each of the closures implemented in the package includes a plot argument such that quick visuals can be obtained using a line of code like this: `sim_R(log_mean = log(500), log_sd = 0.5, plot = TRUE)(years = 1:100)`).

@@

| **Function call**                           | **Description**                                            | **Symbol**                          |
|:------------------------------------------- |:---------------------------------------------------------- | :---------------------------------- |
| `sim_abundance(`                            | &nbsp;                                                     | &nbsp;                              |
| `+  ages = 1:20,`                           | Ages                                                       | $a$                                 |
| `+  years = 1:20,`                          | Years                                                      | $y$                                 |
| `+  R = sim_R(log_mean = log(30000000),`    | Mean recruitment^1^                                        | $\mu_r$                             |
| `+            log_sd = 0.5),`               | Standard deviation of log-recruitment                      | $\sigma_r$                          |
| `+  Z = sim_Z(log_mean = log(0.5),`         | Mean total mortality^2^                                    | $\mu_Z$                             |
| `+            log_sd = 0.2,`                | Standard deviation of total mortality (log)                | $\sigma_Z$                          |
| `+            phi_age = 0.9,`               | Correlation across ages in error around total mortality    | $\varphi_{\delta, \mathrm{age}}$    |
| `+            phi_year = 0.5),`             | Correlation across years in error around total mortality   | $\varphi_{\delta, \mathrm{year}}$   |
| `+  growth = sim_vonB(Linf = 120,`          | Mean asymptotic length (cm)                                | $L_{\infty}$                        |
| `+                    L0 = 5,`              | Length in birth year (cm)                                  | $L_0$                               |
| `+                    K = 0.1,`             | Growth rate                                                | $K$                                 |
| `+                    log_sd = 0.1,`        | Standard deviation of the von Bertalanffy growth curve     | $\sigma_L$                          |
| `+                    length_group = 3))`   | Length group bin size for abundance at length (cm)         | $l_{\mathrm{group}}^{N}$            |

@@

if (is_html) {
  p
} else {
  knitr::include_graphics("figures/plot_surface.png")
}

@@

if (is_html) {
  p
} else {
  knitr::include_graphics("figures/plot_grid.png")
}

@@

In addition to supplying objects produced by `sim_abundance` and `make_grid`, the `sim_distribution` function requires two closures that describe the age-year-space covariance and the relationship with depth. Here we use `sim_ays_covar` and `sim_parabola` to control these relationships and a wide range of age and year specific distributions can be obtained by adjusting a few parameters in these closures (Figure \@ref(fig:distribution)). Though we only provide one option for simulating a spatial noise (see **[S3 Appendix][S3 Appendix: Age-year-space covariance]** for details), advanced users could construct closures that leverage simulation models provided by packages such as **`RandomFields`** [@schlather2020] or **`INLA`** [@rue2009]. Below we run a default `sim_distribution` call, which generates a population that forms tight clusters that are more strongly correlated across years than ages, and another call that generates a population that is more diffuse (i.e. wider `range`) and exhibits stronger correlation across ages than years (i.e. lower `phi_year` and higher `phi_age`). Distributions can also be forced to be the same across ages and years by using the `group_ages` and `group_years` arguments, respectively, in the `sim_ays_covar` closure. Variance in the size of the clusters can also be modified by changing the `sd` argument in the `sim_ays_covar` function. In other words, these parameters can be modified to control the degree of age-specific clustering and inter-annual site-fidelity exhibited by the simulated population. Note that the resolution of the default grid is high and, as such, the simulations below may take minutes to complete. Also note that the key functions in the **`SimSurvey`** package have been set-up to be pipe (`%>%`; [@bache2014]) friendly such that values from one function call are forwarded to the next function (i.e. output from the two calls below are functionally the same though the approach is slightly different).

@@

if (is_html) {
  b_plots
} else {
  knitr::include_graphics("figures/plot_distribution.png")
}

@@

if (is_html) {
  plot_b
} else {
  knitr::include_graphics("figures/plot_survey.png")
}

@@

if (is_html) {
  p
} else {
  knitr::include_graphics("figures/plot_total_strat_fan.png")
}

@@

if (is_html) {
  p
} else {
  knitr::include_graphics("figures/plot_length_strat_fan.png")
}

@@

if (is_html) {
  p
} else {
  knitr::include_graphics("figures/plot_age_strat_fan.png")
}

@@

if (is_html) {
  rank_p
} else {
  knitr::include_graphics("figures/plot_survey_rank.png")
}

@@

if (is_html) {
  surface_p
} else {
  knitr::include_graphics("figures/plot_error_surface.png")
}

@@

if (is_html) {
  p
} else {
  knitr::include_graphics("figures/alt_tests_plots.png")
}

@@

knitr::include_graphics("figures/real_sim_comp.png")

>>>>

library(SimSurvey)
library(plotly)
library(raster)
library(lattice)
library(viridis)
library(data.table)
library(magrittr)
library(here)
Sys.setenv("MAPBOX_TOKEN" = "pk.eyJ1IjoicGF1bHJlZ3VsYXIiLCJhIjoiY2pueGIxejMxMGM0MjNqbjR1aXdwYm92bSJ9.R-t1SCa0VHKf4N-PQmYI5Q")
source("analysis/paper/helper_functions.R")

@@

Here, the `R_vec` object holds 100 years of simulated recruitment values and each run of the `R_fun` function will result in different simulated values using the internal formulation and the parameters supplied to `sim_R`. The other closures included in the package operate in a similar way in that parameter inputs are supplied to the closure and the functions returned by the closure requires inputs such as ages and/or years. This was done to avoid the repeated specifications of key arguments, such as ages and years. Moreover, this approach provides an option for advanced R users to inspect and modify the closures implemented in the package to supply custom closures with alternate equations (see https://paulregular.github.io/SimSurvey/articles/custom_closures.html for a short vignette on creating custom closures). Also note that each of the closures implemented in the package includes a plot argument such that quick visuals can be obtained using a line of code like this: `sim_R(log_mean = log(500), log_sd = 0.5, plot = TRUE)(years = 1:100)`).

@@

| **Function call**                           | **Description**                                            | **Symbol**                          |
|:------------------------------------------- |:---------------------------------------------------------- | :---------------------------------- |
| `sim_abundance(`                            | &nbsp;                                                     | &nbsp;                              |
| `+  ages = 1:20,`                           | Ages                                                       | $a$                                 |
| `+  years = 1:20,`                          | Years                                                      | $y$                                 |
| `+  R = sim_R(log_mean = log(30000000),`    | Mean log recruitment^1^                                    | $\mu_r$                             |
| `+            log_sd = 0.5),`               | Standard deviation of log recruitment                      | $\sigma_r$                          |
| `+  Z = sim_Z(log_mean = log(0.5),`         | Mean log total mortality ^2^                               | $\mu_Z$                             |
| `+            log_sd = 0.2,`                | Standard deviation of log total mortality                  | $\sigma_Z$                          |
| `+            phi_age = 0.9,`               | Correlation across ages in error around total mortality    | $\varphi_{\delta, \mathrm{age}}$    |
| `+            phi_year = 0.5),`             | Correlation across years in error around total mortality   | $\varphi_{\delta, \mathrm{year}}$   |
| `+  growth = sim_vonB(Linf = 120,`          | Mean asymptotic length (cm)                                | $L_{\infty}$                        |
| `+                    L0 = 5,`              | Length in birth year (cm)                                  | $L_0$                               |
| `+                    K = 0.1,`             | Growth rate                                                | $K$                                 |
| `+                    log_sd = 0.1,`        | Standard deviation of the von Bertalanffy growth curve     | $\sigma_L$                          |
| `+                    length_group = 3))`   | Length group bin size for abundance at length (cm)         | $l_{\mathrm{group}}^{N}$            |

@@

if (is_html) {
  p
} else {
  knitr::include_graphics(here("analysis", "paper", "figures", "plot_surface.png"))
}

@@

if (is_html) {
  p
} else {
  knitr::include_graphics(here("analysis", "paper", "figures", "plot_grid.png"))
}

@@

In addition to supplying objects produced by `sim_abundance` and `make_grid`, the `sim_distribution` function requires two closures that describe the age-year-space covariance and the relationship with depth. Here we use `sim_ays_covar` and `sim_parabola` to control these relationships and a wide range of age and year specific distributions can be obtained by adjusting a few parameters in these closures (Figure \@ref(fig:distribution)). While here we only describe one option for simulating a spatial noise (see **[S3 Appendix][S3 Appendix: Age-year-space covariance]** for details), custom colsures can be used that leverage simulation models provided by packages such as **`RandomFields`** [@schlather2020] or **`INLA`** [@rue2009] (see the code behind `sim_ays_covar_sped` [https://github.com/PaulRegular/SimSurvey/blob/master/R/sim_dist_spde.R] for an example of how the `sim_ays_covar` closure was modified to apply a Stochastic Partial Differential Equation approach using the **`INLA`** package). Below we run a default `sim_distribution` call, which generates a population that forms tight clusters that are more strongly correlated across years than ages, and another call that generates a population that is more diffuse (i.e. wider `range`) and exhibits stronger correlation across ages than years (i.e. lower `phi_year` and higher `phi_age`). Distributions can also be forced to be the same across ages and years by using the `group_ages` and `group_years` arguments, respectively, in the `sim_ays_covar` closure. Variance in the size of the clusters can also be modified by changing the `sd` argument in the `sim_ays_covar` function. In other words, these parameters can be modified to control the degree of age-specific clustering and inter-annual site-fidelity exhibited by the simulated population. Note that the resolution of the default grid is high and, as such, the simulations below may take minutes to complete. Also note that the key functions in the **`SimSurvey`** package have been set-up to be pipe (`%>%`; [@bache2014]) friendly such that values from one function call are forwarded to the next function (i.e. output from the two calls below are functionally the same though the approach is slightly different).

@@

if (is_html) {
  b_plots
} else {
  knitr::include_graphics(here("analysis", "paper", "figures", "plot_distribution.png"))
}

@@

if (is_html) {
  plot_b
} else {
  knitr::include_graphics(here("analysis", "paper", "figures", "plot_survey.png"))
}

@@

if (is_html) {
  p
} else {
  knitr::include_graphics(here("analysis", "paper", "figures", "plot_total_strat_fan.png"))
}

@@

if (is_html) {
  p
} else {
  knitr::include_graphics(here("analysis", "paper", "figures", "plot_length_strat_fan.png"))
}

@@

if (is_html) {
  p
} else {
  knitr::include_graphics(here("analysis", "paper", "figures", "plot_age_strat_fan.png"))
}

@@

if (is_html) {
  rank_p
} else {
  knitr::include_graphics(here("analysis", "paper", "figures", "plot_survey_rank.png"))
}

@@

if (is_html) {
  surface_p
} else {
  knitr::include_graphics(here("analysis", "paper", "figures", "plot_error_surface.png"))
}

@@

if (is_html) {
  p
} else {
  knitr::include_graphics(here("analysis", "paper", "figures", "alt_tests_plots.png"))
}

@@

knitr::include_graphics(here("analysis", "paper", "figures", "real_sim_comp.png"))
